---
title: "simulation_exercise"
output: html_document
---

This is an excercise to simulate exponential distribution and run analysis on properties of the distribution of the mean of 40 exponential(0.2)s

```{r}
library(ggplot2)
## exponential distribution rate parameter
lambda <- 0.2

## sample size
n <- 40

## number of observation
obs <- 1000

## calculate the means/variances of 1000 observations
means <- NULL
samples <- NULL
for (i in 1 : obs) {
  samples <- rexp(n, lambda)
  means <- c(means, mean(samples))
  }

## calculate the sample variance of 1000 observation

```

1. Show where the distribution is centered at and compare it to the theoretical center of the distribution.  

Below histogram plots distribution frequency of means of all observations. It shows that the distribution is centered at 5, which is the theoretical center of distribution (mean of exponential distribution = 1/lambda  = 1/0.2 = 5)  

```{r}
hist(means)
```

2. Show how variable it is and compare it to the theoretical variance of the distribution, which is (1/lambda)^2 = 25


```{r}
g <- ggplot(data.frame(x = 1:obs, y = means), aes(x = x, y = y)) 
g <- g + geom_hline(yintercept = 1/lambda, color='red') + geom_line(size = 1)
g <- g + labs(x = "Number of obs", y = "Mean")
g
```